### 2020-09-02 manuscript.tex
typo

Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ was indeed superior on larger datasets (where $L > 2$kb; \textbf{Fig \ref{fig:round4Results}}).
While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the bony fish alignment by Broughton et al.\cite{Broughton_2013}).
The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:parameterisationResults}}) make this dataset the perfect canidate for the NER operator. 
Every proposal acceptance yields a new tree topology and thus facilitates traversal of tree space.

>>>>

Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ was indeed superior on larger datasets (where $L > 2$kb; \textbf{Fig \ref{fig:round4Results}}).
While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the bony fish alignment by Broughton et al.\cite{Broughton_2013}).
The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:parameterisationResults}}) make this dataset the perfect candidate for the NER operator. 
Every proposal acceptance yields a new tree topology and thus facilitates traversal of tree space.
